---
title: "Decision trees homework"
output: html_notebook
---

# Decision trees homework

```{r}
library(rpart)
library(rpart.plot)
library(GGally)
library(broom)
library(janitor)
library(modelr)
library(yardstick)
library(ggplot2)
library(tidyverse)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```


# Data Dictionary

sex: Biological Sex, male or female
age_status: adult or child (child defined as under 16)
class : Ticket class, 1 = 1st (Upper class), 2 = 2nd (Middle Class), 3 = 3rd (Lower Class)
port_embarkation: C = Cherbourg, Q = Queenstown, S = Southampton
sibsp : number of siblings / spouses aboard the Titanic
parch: number of parents / children aboard the Titanic. Some children travelled only with a nanny, therefore parch=0 for them.
survived_flag : did they survive, 0 = No, 1 = Yes

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0, 1)) %>%
  select(-c(X1, passenger_id, name, ticket, fare, cabin)) %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(pclass = factor(pclass, levels = c(3, 2, 1), labels = c("Lower", "Middle", "Upper")),
         survived = factor(survived, levels = c(0, 1), labels = c("did not survive", "survived")),
         age = as.numeric(as.integer(age)),
         age_status = as.factor(if_else(age <= 16, "child", "adult"))) %>% 
  na.omit()
titanic_clean
```

# Having an initial look at potentially siginificant variables

```{r}
ggpairs(titanic_clean, progress = FALSE)
```

potentially be important variables:
pclass
sex
parch
The above shows there is disparity between the box sizes in both pclass and sex with survived plots.

```{r}
dim(titanic_clean)
```

# Creating the test and training data - 20/80 split

```{r}
n_data <- nrow(titanic_clean)
#get an index
test_index <- sample(1:n_data, size = n_data * 0.2)
#get those rows from the actual data
titanic_test <- slice(titanic_clean, test_index)
# get the training dataset
titanic_train <- slice(titanic_clean, -test_index)
```

```{r}
titanic_test %>% 
  tabyl(survived)
```

```{r}
titanic_train %>% 
  tabyl(survived)
```

output tables show a fair balance


#Plotting decision tree
```{r}
titanic_fit <- rpart(survived ~ .,
                     data = titanic_train,
                     method = "class")
```



```{r}
rpart.plot(titanic_fit, yesno = 2)
```

The decision tree shows the important factors are 

sex
pclass
age
sib_sp

The first  shows that there is a 0.39 probability that a passenger did not survive from 100% of training data.

The primary important factor is identified as sex

The second nodes in the hierarchy show that if you are not male you have a 0.72 probability of surviving 36% of training set

If you are male you have a 0.20 probability of not surviving 64% of training set. 

Interesting points

- If you are female and pclass != lower then you have a 0.94 probablity of surviving

- if you are male and under age 13 and have 2 or more siblings you have a 0.94 probabilty of surviving

- if you are a female traveling lower class and below 28 years old with no siblings you have 0.71 chance of surviving (6% of pop)

- if you are male over 13 years old you have 0.17 probility of not surviving

- if you are male, younger than 13 with 2 or more sibilings your probability of survival is the lowest (0.09) and makes up 2% of the population.


```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")
titanic_test_pred
```

```{r}
conf_matrix <- titanic_test_pred %>% 
  conf_mat(truth = survived, estimate = pred)
conf_matrix
```





