---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(selectr)
```

```{r}
code_clan_tweets <- read.csv("data/code_clan_tweets.csv")
code_clan_tweets
```

Question 1 

Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
ncol(code_clan_tweets)
```

```{r}
nrow(code_clan_tweets)
```
```{r}
names(code_clan_tweets)
```

Question 2 

Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).


```{r}
code_clan_tweets %>%
  filter(is_quote == FALSE) %>%
  tally(favorite_count)

```
Question 3 

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

price.cut <- diamonds %>%
group_by(cut) %>%
summarize(Mean = mean(price, na.rm=TRUE))

```{r}
code_clan_tweets %>%
  group_by(source) %>%
  filter(is_quote == FALSE) %>%
  summarise(retweets = mean(retweet_count))
  

```

Question 4 

*Count* the total number of likes (i.e. *total of favourite_count*), **split by media type**, and ***arrange them from most likes*** (desc) to least. Assume that any tweets without a listed media type are of type “text”.


Get the data columbs that i am interested 1. media 2: favorite_count

```{r}
favourite_tweets <- code_clan_tweets %>% 
  select(media_type, favorite_count) 


favourite_tweets
  

```

sum(people$Weight,na.rm=TRUE)

```{r}
code_clan_tweets %>%
  group_by(media_type) %>%
  tally(favorite_count)





8:42
code_clan_tweets %>%
  summarise(tweets = mean(display_text_width))
```


Find the mean number of characters that a CodeClan tweet contains.


```{r}
mean_character <- mean("text") 
mean_character
```





The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")

```
```{r}
as_tibble(code_clan_info)
```

