---
title: "R Notebook"
output: html_notebook
---
## Manual model development

## 1: Tidy up the data ready for regression
 
```{r}
library(car)
library(modelr)
library(GGally)
library(relaimpo)
library(lm.beta)
library(fastDummies)
library(tidyverse)

kc_house_data <- read_csv("data/kc_house_data.csv")

# Check data and look for initial observation

glimpse(kc_house_data)
summary(kc_house_data)
```
Look at data set and find any Na results:

```{r}
kc_house_data %>% 
summarise_all(funs(sum(is.na(.))))

```

Remove any variable that we dont want to use :

```{r}
kc_house_clean <- kc_house_data %>% 
  select(-c(id, date, zipcode, sqft_living15, sqft_lot15,))

```

Changes:
1.waterfront into a logical variable
2.'yr_renovated' into a 'renovated' logical variable
3."condition" & "grade" both apear to be categorical variables, to move forward with my model i will need to use dummy variables. whichi will become true/false.

1:
```{r}
kc_house_clean <- kc_house_clean %>% 
  mutate(waterfront = ifelse(waterfront == 1, T, F))
kc_house_clean
```

2:
```{r}
kc_house_clean <- kc_house_clean %>% 
  mutate(renovated = ifelse(yr_renovated == 0, F, T)) %>% 
  select(-yr_renovated)
kc_house_clean
```

'Condition' and 'Grade' are both categorical variables. To model the data accurately, it is important to create 'dummy variables' for both condition and grade, which are 'true' or 'false' only:

```{r}
houses_clean %>% 
  summarise(min_grade = min(grade), max_grade = max(grade),
            min_condition = min(condition), max_condition = max(condition))
```

```{r}
houses_dummy <- houses_clean %>%
  dummy_cols(select_columns = c("grade", "condition"), remove_first_dummy = T) %>% 
  dplyr::select(-c(condition, grade))
houses_dummy
  
```


