---
title: "R Notebook"
output: html_notebook
---

Load in librarys & data set.


```{r}

```

```{r}
install.packages(stringr)
library(tidyverse)
library(dplyr)
library(stringr)
read_csv("data/books.csv")

```

Rename data set for research

```{r}
books_info <- read.csv("data/books.csv")

books_info
```


Initial reading of data set

```{r}
dim(books_info)
```


```{r}
nrow(books_info)
```

```{r}
ncol(books_info)
```

```{r}
names(books_info)
```

Find missing values 

```{r}
books_info %>%
  select(everything()) %>%
  summarise_all(funs(sum(is.na(.))))
```

Replace/remove missing values

```{r}
books_info2 <- books_info %>% 
  drop_na(ratings_count, text_reviews_count)
books_info2
```

Review/investigate data set

View the data set by only looking at author,average rating, rating count and publisher.

Arrange order by average rating in desc

```{r}
top_rated <- books_info2 %>% 
  select(authors, average_rating, ratings_count)
  arrange(top_rated, desc(average_rating))
top_rated
```
The above data shows that arranginf by the average rating is missleading as some of these results have been rated very few times therefore have a higher average rating.

Lets arrange the same data set by ratings count to compare the average rating to the number of ratings to get a better value.

```{r}
arrange(top_rated, desc(ratings_count)) %>% 
  print
```
The data above lets us see the average rating in desc order compared to the average rating.


Filter only results by author j.k rowling/mary grandpre

```{r}
jkrowling <- filter(books_info2, authors == "J.K. Rowling/Mary GrandPré")

jkrowling
```

Organise above date by rating count in desc order

```{r}
jkrowling_books <-jkrowling %>% 
  select(authors, average_rating, ratings_count)
arrange(jkrowling_books, desc(ratings_count))
```

Arrange by average rating 

```{r}
jkrowling_books %>% 
  select(authors, average_rating, ratings_count)
arrange(jkrowling_books, desc(average_rating))
```

Now lets look at the data that only has over 20000000 or above ratings

```{r}
jk_highest_rated <- jkrowling_books %>% 
  select(average_rating, ratings_count) %>% 
  filter(ratings_count >= 2000000)
jk_highest_rated
```

