---
title: "R Notebook"
output: html_notebook
---

#Day 3 Homework

```{r}
library(tidyverse)
movies <- read_csv("data/movies.csv")
```
view data 

```{r}
movies
```
View in some more detail 

```{r}
head(data)
```

#question 1 notes:

*first i would sort title in desc order to make it easier to follow.
*i would take a look at a couple of different columns to ensure all data in each is in the same format.
*Check for any missing value(na) or out of place values 


#Q2

create subset of data and select what to put in it.
```{r}
movies_selected <- select(movies, title, runtime, budget)

movies_selected
```

#Q3 Find missing values if any in each set

```{r}
movies_selected %>%
  filter(is.na(title))

dim(movies_selected)
```

```{r}
movies_selected %>%
  filter(is.na(runtime))

dim(movies_selected)
```


```{r}
movies_selected %>%
  filter(is.na(budget))

dim(movies_selected)
```

Question 4 

```{r}
movies_runtime <- movies_selected %>%
  select(runtime) %>% 
  mutate(runtime = na_if(runtime, "0"))

movies_runtime
```
Question 5 

```{r}
movies_imputed <- movies_runtime %>%
  mutate(runtime =
           coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed
```
 
 slice_min(.data, order_by, ..., n, prop, with_ties = TRUE)
 
 new_coders %>% 
  slice_max(last_yr_income, n = 5)

 #Question 6
 
```{r}
movies_selected %>% 
  slice_min(movies_imputed, n - 10)

```
 question 7 
 
```{r}

```
 

