
This homework is revision from today's class. We will practice what we've learned about dates, times, and time series.

You'll need to copy and run the following code chunk for this homework:

```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(tsibble)
library(tsibbledata)
library(feasts)

date_one <- ymd_hms("2017-04-22 22:01:18")
date_two <- ymd_hms("2001-11-07 10:09:56")
```

 

```{r}
library(nycflights13)
```

# Dates and Times

#Question 1 

Extract the different components (year, month, mday, yday, wday) from the variable datel. Add the labels to the month and do not abbreviate the month labels. 

```{r}
#year
#month
#mdayyday
#wday

#dont abbreviate month = 

month(date_one, label = TRUE, abbr = FALSE)

year(date_one)
mday(date_one)
yday(date_one)
wday(date_one)

```
#Question 2 

Add 14 days to your date 1 variable and store it in a variable called next_fortnight. 
Take away 10 years from your date2 variable, and store it in previous_decade. 

add 14 days:

```{r}
two_weeks_later <- date_one + days(14)
```

Take away 10 years:

```{r}
ten_years_earlier <- date_two - years(10)
```

#Question 3  

Create a variable called this_year which contains today's date. Then create an interval object which uses this_year and the previous_decade variable you made above. Store it in interval_years. 
  
this year:

```{r}
this_year <- today()
```
interval object:
 
```{r}
interval_years <- lubridate::interval(this_year, ten_years_earlier)
```

```{r}
as.period(interval_years)

```

#Question 4   

Change the time zone of both your date variables to "America/New_York", and call them nyc_date1 and nyc_date2. 

change time zone date 1&2

```{r}
nyc_date1 <- ymd_hms("2017-04-22 22:01:18", tz = "America/New_York")
nyc_date2 <- ymd_hms("2001-11-07 10:09:56", tz = "America/New_York")
```

#Question 5  

Use the flights data from the nycflights13 dataset. Make a date-time column called departure_date from the year, month, day, hour, and minute` variables in the flights tibble.

load data

```{r}
library(nycflights13)

```

departure_date col:

```{r}
flights %>% 
  select(year,
         month,
         day,
         hour,
         minute) %>% 
  mutate(departure = make_datetime(year,
                                   month,
                                   day,
                                   hour,
                                   minute))

```

#Part 2
#Time series familiarity 

#Question 6 

Start with the weather data from the nycflights13 package. Select all the variables related to temperature, humidity, and precipitation, and pick out the key and index variables. Have a look at your data, and write a small description of the time series you observe. 

look at data:

```{r}
nycflights13::weather
```

temperature variables selected from tibble:

```{r}
weather_data <- nycflights13::weather
```

```{r}
weather_data_selected <- weather_data %>% 
  select(origin,
         time_hour,
         temp,
         humid,
         precip)

head(weather_data_selected)
```

time observation:

In this selected data we can see the time is recorded on every hour.

#Question 7

Change the weather data into a tsibble. Hint, look up in the notes where we suggest using as_tsibble function. You'll need to define an index and key.

weather_data_tbble :

```{r}
weather_data_tbble <- weather_data_selected %>% 
    as_tsibble(index = time_hour, key = origin)
weather_data_tbble
```
#Question 8 
add cols:

```{r}
weather_data_tbble <- weather_data_tbble %>% 
  mutate(year = year(time_hour),
         month = month(time_hour))

```

Plot using ggplot:

```{r}
weather_data_tbble %>% 
ggplot(aes(x = time_hour, y = temp, group = origin))+ 
  geom_line(aes(colour = origin))

```


#Question 8

Add a year and month column to your new tsibble weather data, and create a basic line plot which shows the temperature data from each airport over time. Have a think back to what you learned in visualisation week, and think about whether plotting the whole time series in one go is adequate here? Write down your suggestions for what could be done to make a better and more informative plot. 




