---
title: "R Notebook"
output: html_notebook
---

# Week_6_day_1_homework

#Q1
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

No of total outcomes =6
No of favorable outcomes =4 {1, 2, 3, 4}
Prob < 5 is = 4/6 = 2/3

Q2
How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

#Q1 If I roll a six-sided dice once, what is the probability of getting a number less than 5?

No of total outcomes =6
No of favorable outcomes =4 {1, 2, 3, 4}
Prob < 5 is = 4/6 = 2/3 

#Q2 How many outcomes are there in the sample space of an experiment in which we toss three dice?

3 dice = 6 x 6 x 6 = 216
```{r}
roll_three_dice <- rolldie(3)
roll_three_dice %>% 
    summarise(size_of_s = n())


```

#Q3 In an experiment where we roll four dice:

4 dice = 6 x 6 x 6 x 6 = 1296
```{r}
roll_four_dice <- rolldie(4)
roll_four_dice %>% 
  summarise(size_of_s = n())

```
#Q3.1 How many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)? 

```{r}
total_equals <- roll_four_dice %>%
  mutate(sum_of_rolls = X1 + X2 + X3 + X4) %>%
  filter(sum_of_rolls == 5 | 
           sum_of_rolls == 6 | 
           sum_of_rolls == 7)
  
total_equals <- total_equals %>%
  group_by(sum_of_rolls) %>%
  summarise(combination_roll = n())
total_equals
```

#Q3.2 what is the probability of this event?


#Q3.3 what assumptions do we apply in answering part ii? 

Outcomes may not happen in all three events, therefore there is no link of events A & B & C. 


#Q4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

Work out possible combinations first:

```{r}
people <- 5
chairs <- c("A","B", "C", "D", "E")
five_people_on_chairs <- permutations(n = 5, r = 5, v = chairs, repeats.allowed = FALSE)

five_people_on_chairs <- as_tibble(five_people_on_chairs)
nrow(five_people_on_chairs)
```

Combinations = 120 possible combinations.
Possibilites they sit in height order = 1
  1. c(A, B, C, D, E) 
  = 1/120
  =0.008333333


# 5. I roll six dice:

```{r}
roll_six_dice <- rolldie(6)
nrow(roll_six_dice)
```

#Q5.1.1what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

is 1/46656 = 0.00002143347 

what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

#????

```{r}
one_to_six <- c(6,5,4,3,2,1)


roll_six_dice_answer  <- roll_six_dice %>% 
  filter(isin(.,one_to_six, ordered = FALSE))
nrow(roll_six_dice_answer)
```
Possible ooutcomes = 720
                   = possible outcomes/total outcomes of six 
                   =720/46656
                   
#Q6 If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

52 cards,
2 colours,
4 suites,
Black cards = 2 suites
Spades/Clubs 
Black cards = 52/2/2        
            = 13
            =13/52
            = 0.25

#Q7 Eight patients: Alice, Bob, Carmen, Dinesh, Ella, Fergus, Gianna and Henry are waiting to see a doctor, but only five appointment slots are left today.

#Q7.1 In how many different orders can the doctor see patients today?
Make vector for patients
use permutations to find order
```{r}
patients_names <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry" )

patients_order <- as.tibble(
  permutations(length(patients_names), 5, v = patients_names, repeats.allowed = FALSE))
  
  
nrow(patients_order)
```

#Q7.2What is the probability of Gianna and Danesh both being seen today?




 
