---
title: "R Notebook"
output: html_notebook
---
##Question 1.

#Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.
```{r}
library(tidyverse)
library(CodeClanData)
backpack
```
##Question 2.

#What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack, aes(x = year, y = backpack_weight))+
  geom_point()
```
##Question 3.
#Are there differences in backpack weight between sex?

```{r}
ggplot(backpack, aes(x = year, y = backpack_weight, colour = sex))+
  geom_point()
```
#split male/female:
```{r}
ggplot(backpack, aes(x = year, y = backpack_weight, colour = sex))+
  geom_point()+
  facet_wrap(~sex)
```
#There is a slight difference in the weights of bag bwtween males/females. from backpack_weight > 15 there are alot more males who are carrying these weights of bag.

##Question 4.

#What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack)+
  aes(x = body_weight, y = backpack_weight)+
  geom_point()
  
```
###write comments about above

##Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
```{r}
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = sex) + 
  geom_point() + 
  facet_wrap(~sex) + 
    labs(x = "body weight", y = "backpack weight")
```

This above plots show that in general males tend to carry slighly heavier bags but are also slighlty heavier in body weight.




##Question 8.
#Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.
?

#Try both backpack_weight and body_weight as well as the ratio.
#Hint: faceting would be useful here.
??
