---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)
salaries <- read_csv("~/codeclan_homework_jonnyb/week_04/dplyr_practice_hw/data/salaries.csv")
salaries
```
#Use select to see the beginning salary variable and the current salary variable.

```{r}
select(salaries, "beginning_salary", "current_salary")

```

#Use filter to see the employees aged over 50, who have a salary over £20,000.

```{r}
filter(salaries, "age" == ("current_salary" <= 20000
                           ))
```

#Use arrange to order by the data so that the highest salaries are first.

```{r}
arrange(salaries, desc(current_salary))
```


#Use mutate to make a new variables beginning_salary_pence and current_salary_pence. These should have the corresponding salaries in pence instead of pounds.

```{r}
mutate(salaries, beginning_salary_pence = beginning_salary*100,
           current_salary_pence   = current_salary*100)

```


#Use summarise to find the maximum age and the minimum age.


```{r}
summarise(salaries, max_age = max(age),
              min_age = min(age))
```

#Find the minimum salary and the maximum salary.

```{r}
summarise(salaries, min_salary = min(current_salary),
              max_salary = max(current_salary))
```


#Find all the employees aged under 30.

```{r}
filter(salaries, age < 30)
```


#Order the data in terms of increasing educational level where ties are broken using age.


```{r}
arrange(salaries, educational_level, age)
```

#9
```{r}
select(salaries, -gender, -employment_category, -is_white)
```

#10

```{r}
filter(salaries, work_experience < 2 | educational_level < 12)
```

#11
?

#12
?')



### Pipes

```{r}
salaries %>%
  filter(educational_level < 17) %>%
  group_by(educational_level) %>%
  summarise(mean_salary = mean(current_salary)) %>%
  arrange(desc(mean_salary))
```
2. 

```{r}
salaries %>%
  filter(work_experience > 2) %>%
  group_by(gender, employment_category) %>%
  summarise(mean_salary = mean(current_salary))
```
```{r}
salaries %>%
  group_by(employment_category) %>%
  summarise(mean_salary = mean(current_salary),
            median_salary = median(current_salary)) %>%
  mutate(difference = mean_salary - median_salary) %>%
  arrange(desc(difference))
```

