---
title: "R Notebook"
output: html_notebook
---
#Day 2 Hw 

1:Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r}
library(tidyverse)
library(mosaicData)
library(GGally)
library(ggfortify)
library(mosaic)
library(fastDummies)

diamonds <- read_csv("diamonds.csv")

glimpse(diamonds)

```
#part2: We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r}
diamonds %>% 
  select(carat, x, y, z) %>% 
  ggpairs(diamonds)
```

part3:Sowe do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}
diamonds <- diamonds %>% 
  select(-x, -y, -z)
glimpse(diamonds)
```
part 4:We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.

4.1Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}
ggpairs(diamonds)


```

part 4.2:Perform further ggplot visualisations of any significant correlations you find.


```{r}
diamonds %>% 
  ggplot(aes(x = price, y = carat)) +
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

```
Part 5.1:

Shortly, we may try a regression fit using one or more of the categorical predictors; cut, clarity and color, so let’s investigate these predictors:

Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

```{r}
diamonds %>% 
  distinct(cut) 
diamonds %>% 
  distinct(color)
diamonds %>% 
  distinct(clarity)
```


```{r}

diamonds_dummy1 <- diamonds %>% 
  dummy_cols(select_columns = c("cut", "color", "clarity"), remove_first_dummy = TRUE,
             remove_selected_columns = TRUE)
```

```{r}
diamonds_dummy1

```

```{r}

```

