---
title: "R Notebook"
output: html_notebook
---

# Part 1

### Load in libraries and data

```{r}

library(relaimpo)
library(modelr)
library(GGally)
library(lm.beta)
library(janitor)
library(lubridate)
library(fastDummies)
library(tidyverse)
avocado <- read_csv("data/avocado.csv") %>% 
  clean_names()
```
Initial look at data:
```{r}
glimpse(avocado)
summary(avocado)
view(avocado)
```

I have chosen to build an explanatory model for the average_price.

#Tidying avocado 
group the region data to make it easier to use

i looked into the region and decide to group by "east", "mid_west" & "west" to try shorten the lenth of thid data set and make it easier to interperate

```{r}
avocado_clean <- avocado %>% 
  select(-c(x1, date, year)) %>% 
  mutate(region = as.character(region)) %>% 
  mutate(region = if_else(str_detect(region,
 "Albany|BaltimoreWashington|BuffaloRochester|Boston|Charlotte|Detroit|HarrisburgScranton|HartfordSpringfield|Indianapolis|Jacksonville|Nashville|NewYork|Northeast|NorthernNewEngland|Orlando|Philadelphia|Pittsburgh|RichmondNorfolk|Roanoke|SouthCarolina|Southeast|Syracuse|Tampa|MiamiFtLauderdale|Atlanta"), "east", region)) %>% 
  mutate(region = if_else(str_detect(region,
 "Chicago|CincinnatiDayton|DallasFtWorth|Denver|Houston|Columbus|GreatLakes|Louisville|GrandRapids|Midsouth|NewOrleansMobile|Plains|StLouis"), "mid_west", region)) %>% 
   mutate(region = if_else(str_detect(region,
 "Boise|California|DallasFtWorth|Denver|Houston|LasVegas|LosAngeles|PhoenixTucson|Portland|RaleighGreensboro|Sacramento|SanDiego|SanFrancisco|Seattle|SouthCentral|Spokane|WestTexNewMexico"), "west", region)) %>% 
  mutate(region = as.factor(region))

glimpse(avocado_clean)
  
```


```{r}
avocado_clean %>% 
  ggplot(aes(x = region, y = average_price)) +
  geom_boxplot()
```
The above data shows little difference un region so i have decided to drop the Rgion data and look into other variabkles
```{r}
avocado_clean <- avocado_clean %>% 
  select(-region)
```

Check region has been dropped
```{r}
glimpse(avocado_clean)
```

Now i will drop all NA values to make the further analysis easier. 
```{r}
avocado_trimmed <- avocado_clean %>% 
  drop_na()
dim(avocado_trimmed)
```

Looking at the distribution for average_price:
```{r}
avocado_trimmed %>% 
  ggplot(aes(average_price))+
  geom_histogram()
``` 

Check for alias variables in data set

```{r}
alias(average_price ~ ., data = avocado_trimmed)
```

the above shows that we have no alias variable pressent within the data set.

Finding correlation between variables and average_price

```{r}
ggpairs(avocado_trimmed)
```
Few of numeric variables show particularly strong correlation with average_price.

The highest correlation value is x4046 - 0.208 followed by total_volume - 0.193

The boxplot for type and average price shows separation between the two variable types.


# 1st predictor model building :

x4046 and average_price model 

```{r}
mod1a <- mod1a <- lm(average_price ~ x4046, data = avocado_trimmed)
summary(mod1a)
```

Residual standard error: 
0.3939 on 18247 degrees of freedom
Multiple R-squared:  0.0434

```{r}
par(mfrow = c(2,2))
plot(mod1a)
```

The residuals v fitted & scale-location plots show two different clusters in each diagram and a clear pattern.

total_volume & average_price model 

```{r}
mod1b <- mod1b <- lm(average_price ~ total_volume, data = avocado_trimmed)
summary(mod1b)
```

Residual standard error: 0.3951 on 18247 degrees of freedom
Multiple R-squared:  0.03715

Higher RSE and lower r-sq value than mod1a

```{r}
par(mfrow = c(2,2))
plot(mod1b)
```

The residual v fitted & scale-location plots show clear patterns.



# 2nd Predictor

Adding residuals from mod1a and removing average_price and x4046

```{r}
avocado_res <- avocado_trimmed  %>% 
  add_residuals(mod1a) %>% 
  select(-c(average_price, x4046))
```

```{r}
ggpairs(avocado_res)
```

There appears to be no other variable that correlates particularly with the residuals apart from type.

```{r}
mod2 <- lm(average_price ~ x4046 + type, data = avocado_trimmed)
summary(mod2)
```

Residual standard error: 0.316 on 18246 degrees of freedom
Multiple R-squared:  0.3843

RSE is down from mod1a and r-sq value is greater too indicating a better model

```{r}
par(mfrow = c(2,2))
plot(mod2)
```

Plots show points in vertical line due to categorical data type.

Adding interaction

```{r}
mod3 <- lm(average_price ~ x4046 + type + x4046:type, data = avocado_trimmed)
summary(mod3)
```

Residual standard error: 0.3148 on 18245 degrees of freedom
Multiple R-squared:  0.3891

RSE is down from mod2 and r-sq value is greater too, indicating better model.

Testing relative importance

```{r}
calc.relimp(mod3, type = "lmg", rela = TRUE)
```

Type  looks to be by far the most important factor in regards to average_price.
lmg value is 92.5% 
