---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

```{r}
house_sales <- read_csv("ames.csv")  %>% 
  clean_names()

glimpse(house_sales)
dim(house_sales)
```

Obsevations = 2930
variables = 82

```{r}
house_sales %>% 
  head()
```



#Distribution of lot areas

lot_area plot:

```{r}
lot_areas <- house_sales %>% 
  select(lot_area)

lot_areas %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(fill = "grey30", colour = "white", bins = 30) +
  labs(x = "Lot Area",
       y = "Count",
       title = "Distribution of lot areas") 
```


```{r}
lot_areas %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(fill = "grey30", colour = "grey30", bins = 100) +
  labs(x = "Lot Area",
       y = "Count",
       title = "Distribution of lot areas") 
```

There is more detail in this plot. It may be that the distribution of lot areas
under 25000 produces a normal distribution, but for the whole data, this can't
be discerned.

# Calculating a mean lot area
.

```{r}
mean_sample_lot_area <- lot_areas %>% 
    specify(response = lot_area) %>% 
    generate(reps = 1000, type = "bootstrap") %>% 
    calculate(stat = "mean")
mean_sample_lot_area %>% 
  ggplot() +
  aes(stat) + 
  geom_histogram(colour = "white", bins = 30) + 
  labs(x = "Mean lot area",
       y = "",
       title = "Distribution of means ") 
```

### Calculate Confidence Interval


```{r}
infer_ci_95 <- mean_sample_lot_area %>% 
  get_ci()
infer_ci_95
```


```{r}
mean_sample_lot_area %>% 
  visualise() +
  shade_ci(endpoints = infer_ci_95) +
  labs(x = "Mean lot area",
       y = "",
       title = "Distribution of  means ")
```


```{r}

infer_ci_99 <- mean_sample_lot_area %>% 
  get_ci(level = 0.99, type = "percentile")
infer_ci_99
```

Creating a plot with 99% CI
```{r}
mean_sample_lot_area %>% 
  visualise() +
  shade_ci(endpoints = infer_ci_99) +
  labs(x = "Mean lot area",
       y = "",
       title = "Distribution of  means ") 
```

As expected, the CI is wider (more of the distribution is within the 99% CI)

Finally, the best estimate of the mean can be calculated. For completeness,
the lower CI boundary and upper CI boundary have been included.

```{r}
mean_sample_lot_area %>% 
  summarise(best_estimate_mean = mean(stat)) %>% 
  bind_cols(infer_ci_95)
```
